### 2024-09-18 decision-making.qmd
20240918 - betting markets for football

- <https://www.predictit.org>
- <https://polymarket.com>
- <https://www.rotowire.com/betting/nfl/player-futures.php>

>>>>

- <https://www.predictit.org>
- <https://polymarket.com>

There are also betting markets for football:

- <https://www.rotowire.com/betting/nfl/player-futures.php>
- <https://vegasprojections.com>
- <https://www.actionnetwork.com/nfl/props>
